Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-22 article.rnw
Remove a completed TODO.
Add missing references for the first paragraph of the introduction.

Models have long been used in community ecology \parencite{lotka1925elements}.
They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing} or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{XXX}.

@@

	\caption{%
		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}). %TODO: Debug this.
		\Subref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
		Species have been reordered that species which are grouped together appear adjacent.
		The ordering is the same in \subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} as shown in \subref{fig:best-alpha-matrix}.
	}
	\label{fig:best-model}
\end{figure}

>>>>

Models have long been used in community ecology \parencite{lotka1925elements}.
They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing} or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{gilman2010framework, sutherst2007including}.

@@

	\caption{%
		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}).
		\Subref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
		Species have been reordered that species which are grouped together appear adjacent.
		The ordering is the same in \subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} as shown in \subref{fig:best-alpha-matrix}.
	}
	\label{fig:best-model}
\end{figure}
